---
title: "# README for Data Science Exam"
author: "Tapiwa-24986143"
date: "2025-06-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## General Notes
This project follows a functional programming approach. Each question is in its own folder with associated code/scripts and outputs saved separately. 

Question 1 – Name Surges & Cultural Influence
Objective:
Identifying names with the largest year-on-year increases and explore whether these spikes correlate with pop culture trends using Billboard and HBO datasets.

Data Loading & Preparation
```{r}
# Load the datasets 
Baby_Names <- read_rds("data/US_Baby_names/Baby_Names_By_US_State.rds")
Top_100_Billboard <- read_rds("data/US_Baby_names/charts.rds")
HBO_titles <- read_rds("data/US_Baby_names/HBO_titles.rds")
HBO_credits <- read_rds("data/US_Baby_names/HBO_credits.rds")

glimpse(Baby_Names)

# Extracting top 25 names per year and gender across all states
top_25_names <- Baby_Names %>%
  group_by(Year, Gender, Name) %>%
  summarise(Total = sum(Count), .groups = "drop") %>%
  group_by(Year, Gender) %>%
  slice_max(order_by = Total, n = 25) %>%
  mutate(Rank = rank(-Total)) %>%
  select(Year, Gender, Name, Rank)
```

Surge Identification
- Grouped by name, gender, and year to calculate total baby counts.
  Calculated year-on-year (YoY) change for each name.
  Selected the top 10 surging names based on highest YoY % increase.

- Rank correlations
  A plot was created to assess whether popular names persist across years.
  This was done by generating a heatmap of rank correlations to compare the top 25 boys' and girls' names in each year with those in the following 3 years.

```{r}
# Function to get spearman correlations between current year and year +1/2/3
get_spearman_for_year <- function(y, g) {
  base_year <- top_25_names %>% 
    filter(Year == y, Gender == g)
  
  result <- tibble()
  
  for (offset in 1:3) {
    compare_year <- top_25_names %>%
      filter(Year == y + offset, Gender == g)
    
    # Join on Name to keep only common names
    joined <- inner_join(base_year, compare_year, by = "Name", suffix = c("_base", "_comp"))
    
    if (nrow(joined) >= 5) {
      rho <- cor(joined$Rank_base, joined$Rank_comp, method = "spearman")
    } else {
      rho <- NA
    }
    
    result <- bind_rows(result, tibble(
      Year = y,
      Gender = g,
      Offset = offset,
      Future_Year = y + offset,
      Spearman = rho
    ))
  }
  
  return(result)
}

# Now we apply across all years
years <- unique(top_25_names$Year)
genders <- unique(top_25_names$Gender)

# Apply function to all (year, gender) pairs
correlation_results <- map_dfr(years, function(y) {
  map_dfr(genders, function(g) {
    get_spearman_for_year(y, g)
  })
})
```

Visualization
```{r}
ggplot(correlation_results, aes(x = Year, y = Spearman, color = as.factor(Offset))) +
  geom_line() +
  facet_wrap(~Gender) +
  labs(
    title = "Spearman Rank Correlation of Top 25 Baby Names Over Time",
    subtitle = "Correlation between each year's rankings and the next 3 years",
    x = "Base Year",
    y = "Spearman Correlation",
    color = "Years Ahead"
  ) +
  theme_minimal()

ggsave("Figures/spearman_name_correlation.png", width = 10, height = 6)
```

Finding insights on surges : 
- Summarizing total counts per name, year, and gender
```{r}
name_trends <- Baby_Names %>%
  group_by(Name, Year, Gender) %>%
  summarise(Total = sum(Count), .groups = "drop") %>%
  arrange(Name, Gender, Year)
```

- Calculating year-on-year percentage change
```{r}
name_trends <- name_trends %>%
  group_by(Name, Gender) %>%
  mutate(YoY_change = 100 * (Total - lag(Total)) / lag(Total)) %>%
  ungroup()
```

- Top 10 surges by % increase (removing very low baselines)
```{r}
top_surges <- name_trends %>%
  filter(!is.na(YoY_change), lag(Total) >= 50) %>%
  arrange(desc(YoY_change)) %>%
  slice_head(n = 10)
```

\newpage

Visualizing the surges
```{r}
ggplot(top_surges, aes(x = Year, y = Total, color = Name)) +
  geom_line() +
  facet_wrap(~ Name + Gender, scales = "free_y") +
  labs(title = "Top Name Surges Over Time",
       y = "Total Babies Given Name",
       x = "Year") +
  theme_minimal()

ggsave("Figures/top_name_surges.png", width = 10, height = 6)
```

\newpage

Adding Billboard and HBO links to top_surges data: 
- Adding Billboard matches
```{r}
top_surges <- top_surges %>%
  rowwise() %>%
  mutate(
    Billboard_Song_Match = any(str_detect(Top_100_Billboard$song, regex(Name, ignore_case = TRUE))),
    Billboard_Artist_Match = any(str_detect(Top_100_Billboard$artist, regex(Name, ignore_case = TRUE)))
  ) %>%
  ungroup()
```

Join HBO credits and titles
```{r}
hbo_data <- HBO_credits %>%
  left_join(HBO_titles, by = "id")
```

Add HBO matches
```{r}
top_surges <- top_surges %>%
  rowwise() %>%
  mutate(
    HBO_Name_Match = any(str_detect(hbo_data$name, regex(Name, ignore_case = TRUE))),
    HBO_Character_Match = any(str_detect(hbo_data$character, regex(Name, ignore_case = TRUE)))
  ) %>%
  ungroup()

colnames(top_surges)

top_surges_summary <- top_surges %>%
  mutate(
    Billboard_Link = if_else(
      is.na(Billboard_Song_Match) & is.na(Billboard_Artist_Match),
      FALSE,
      TRUE
    ),
    HBO_Link = if_else(
      is.na(HBO_Name_Match) & is.na(HBO_Character_Match),
      FALSE,
      TRUE
    )
  ) %>%
  select(Name, Gender, Year, YoY_change, Billboard_Link, HBO_Link)
```

View and save Table
```{r}
top_surges_summary
write.csv(top_surges_summary, "Figures/top_surges_summary.csv", row.names = FALSE)
```

\newpage

Question 2 : Coldplay vs Metallica
This analysis explores musical trends using Spotify and other music datasets. Specifically, I compared the musical journey and popularity of Coldplay and Metallica, two globally recognized bands with different stylistic and generational appeal.

Data Loading
```{r}
coldplay <- read_csv("data/Coldplay_vs_Metallica/Coldplay.csv")
metallica <- read_csv("data/Coldplay_vs_Metallica/metallica.csv")
spotify_trends <- read_rds("data/Coldplay_vs_Metallica/Broader_Spotify_Info.rds")
billboard_100 <- read_rds("data/Coldplay_vs_Metallica/charts.rds")
```

Data Cleaning and Harmonization
```{r}
coldplay_clean <- coldplay %>%
  select(
    name,
    album = album_name,
    release_date,
    popularity,
    duration = duration,      # assuming already in seconds
    energy,
    tempo,
    valence,
    danceability,
    acousticness,
    liveness,
    speechiness,
    loudness
  ) %>%
  mutate(band = "Coldplay")
# Clean Metallica
metallica_clean <- metallica %>%
  select(
    name,
    album,
    release_date,
    popularity,
    duration_ms,
    energy,
    tempo,
    valence,
    danceability,
    acousticness,
    liveness,
    speechiness,
    loudness
  ) %>%
  # Convert duration_ms safely
  mutate(
    duration_sec = duration_ms / 1000,
    band = "Metallica"
  )
```

Combine data
```{r}
combined_bands <- bind_rows(coldplay_clean, metallica_clean)
combined_bands <- combined_bands %>%
  mutate(album_clean = stri_replace_all_regex(album, "[^\x20-\x7E]", "")) %>%  # Remove non-ASCII characters
  mutate(album_wrapped = str_wrap(album_clean, width = 20))

```

Exploratory Visualization
```{r}
ggplot(combined_bands, aes(x = reorder(album_wrapped, popularity, median), y = popularity, fill = band)) +
  geom_boxplot() +
  coord_flip() +
  facet_grid(band ~ .) +
  labs(
    title = "Popularity Distribution by Album",
    subtitle = "Spotify Popularity Scores for Coldplay and Metallica",
    x = "Album",
    y = "Popularity Score"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.y = element_text(size = 9),
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", size = 14),
    legend.position = "none"
  )

ggsave("Figures/popularity_by_album_initial.png", width = 10, height = 6, dpi = 300)

```

We can get more meaningful figures if we simplify album names
```{r}
library(stringi)

combined_bands <- combined_bands %>%
  mutate(album_clean = stri_replace_all_regex(album, "[^\x20-\x7E]", "")) %>%
  mutate(album_short = str_trunc(album_clean, 25, side = "right"))

# Plot
ggplot(combined_bands, aes(x = popularity, y = reorder(album_short, popularity), fill = band)) +
  geom_boxplot(outlier.size = 0.5) +
  facet_wrap(~band, scales = "free_y") +
  labs(
    title = "Popularity Distribution by Album",
    subtitle = "Spotify Popularity Scores for Coldplay and Metallica",
    x = "Popularity Score",
    y = "Album"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.y = element_text(size = 8),
    strip.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )
ggsave("Figures/popularity_distribution_by_album.png", width = 12, height = 8)
```

\newpage

Looking at longegivity 
```{r}
# Average popularity by year
library(dplyr)
library(ggplot2)

band_trends <- bind_rows(coldplay_clean, metallica_clean) %>%
  mutate(year = lubridate::year(release_date)) %>%
  group_by(band, year) %>%
  summarise(avg_popularity = mean(popularity, na.rm = TRUE), .groups = "drop")

# Plot it
ggplot(band_trends, aes(x = year, y = avg_popularity, color = band)) +
  geom_line(size = 1.2) +
  labs(
    title = "Average Song Popularity Over Time",
    subtitle = "Trend in Spotify Popularity for Coldplay and Metallica",
    x = "Release Year",
    y = "Average Popularity Score",
    color = "Band"
  ) +
  theme_minimal(base_size = 13)

ggsave("Figures/avg_popularity_by_year.png", width = 10, height = 6)

```

Comparing track duration and tempo between the 2 bands
```{r}
# Duration in seconds was already created as duration_sec
# Density plot: Track Duration
ggplot(combined_bands, aes(x = duration_sec, fill = band)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Distribution of Track Duration",
    x = "Duration (seconds)",
    y = "Density",
    fill = "Band"
  ) +
  theme_minimal()

# Save the plot
ggsave("Figures/track_duration_distribution.png", width = 8, height = 5)
```

Density plot: Tempo
```{r}
ggplot(combined_bands, aes(x = tempo, fill = band)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Distribution of Track Tempo",
    x = "Tempo (BPM)",
    y = "Density",
    fill = "Band"
  ) +
  theme_minimal()

# Save the plot
ggsave("Figures/track_tempo_distribution.png", width = 8, height = 5)
```

Next Metric : Energy
Plot energy distribution
```{r}
ggplot(combined_bands, aes(x = energy, fill = band)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Distribution of Track Energy",
    subtitle = "Comparison of Coldplay and Metallica",
    x = "Energy",
    y = "Density",
    fill = "Band"
  ) +
  theme_minimal()

# Save the plot
ggsave("Figures/track_energy_distribution.png", width = 8, height = 5)
```

Valence distribution
Plot valence distribution
```{r}
ggplot(combined_bands, aes(x = valence, fill = band)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Distribution of Track Valence",
    subtitle = "Comparison of Emotional Positivity in Coldplay and Metallica Tracks",
    x = "Valence (Emotional Positivity)",
    y = "Density",
    fill = "Band"
  ) +
  theme_minimal()

# Save the plot
ggsave("Figures/track_valence_distribution.png", width = 8, height = 6)
```

Plot danceability
```{r}
colnames(combined_bands)
ggplot(combined_bands, aes(x = danceability, fill = band)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Distribution of Track Danceability",
    subtitle = "Comparison of Coldplay and Metallica",
    x = "Danceability",
    y = "Density",
    fill = "Band"
  ) +
  theme_minimal()

ggsave("Figures/track_danceability_distribution.png", width = 8, height = 5)
```

Plot Loudness Distribution
```{r}
ggplot(combined_bands, aes(x = loudness, fill = band)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Distribution of Track Loudness",
    subtitle = "Comparison of Coldplay and Metallica",
    x = "Loudness (dB)",
    y = "Density",
    fill = "Band"
  ) +
  theme_minimal()

# Save plot
ggsave("Figures/track_loudness_distribution.png", width = 10, height = 6)
```

Summary key audio features per band
```{r}
feature_summary <- combined_bands %>%
  group_by(band) %>%
  summarise(
    avg_valence = mean(valence, na.rm = TRUE),
    avg_energy = mean(energy, na.rm = TRUE),
    avg_tempo = mean(tempo, na.rm = TRUE),
    avg_danceability = mean(danceability, na.rm = TRUE),
    avg_loudness = mean(loudness, na.rm = TRUE),
    avg_duration_sec = mean(duration_sec, na.rm = TRUE)
  )
```

Save the table
```{r}
write.csv(feature_summary, "Figures/audio_feature_summary.csv", row.names = FALSE)
```

\newpage

# Question 3: Netflix Content Analysis

This analysis investigates what content succeeds on Netflix, using metadata from IMDb and Netflix’s public catalog. The goal is to guide a new streaming startup by identifying the genres, themes, and formats most associated with highly-rated content.

---

## Files

- **Data/**: Raw input files (`titles.rds`, `credits.rds`, `netflix_movies.csv`)
- **Figures/**: All plots saved from the analysis
- **Question 3 paper.Rmd**: Full write-up with visual interpretation and citations

---

## Setup and Packages
```{r}
library(tidyverse)
library(lubridate)
library(stringr)
library(tidytext)
library(tidyr)
```

1) Data Cleaning and Structuring
I began by loading and cleaning the data:
```{r}
titles <- read_rds("Question 3/Data/netflix/titles.rds")
credits <- read_rds("Question 3/Data/netflix/credits.rds")
movie_info <- read_csv("Question 3/Data/netflix/netflix_movies.csv")
```

Cleaning and Structuring
```{r}
titles_clean <- titles %>%
  mutate(
    genres = str_replace_all(genres, "\\[|\\]|'", ""),
    genres = str_split(genres, ",\\s*"),
    country = str_replace_all(production_countries, "\\[|\\]|'", ""),
    country = str_split(country, ",\\s*"),
    release_decade = floor(release_year / 10) * 10
  )

movie_info_clean <- movie_info %>%
  mutate(
    duration_min = as.numeric(str_extract(duration, "\\d+")),
    listed_in = str_split(listed_in, ",\\s*")
  )
```

2) Most Common Genres by Country
I looked at the most frequent genres in Netflix content across the top six contributing countries.
```{r}
top_countries <- movie_info_clean %>%
  filter(!is.na(country)) %>%
  separate_rows(country, sep = ",\\s*") %>%
  count(country, sort = TRUE) %>%
  slice_max(n, n = 6) %>%
  pull(country)

genre_country <- movie_info_clean %>%
  filter(!is.na(country), !is.na(listed_in)) %>%
  separate_rows(country, sep = ",\\s*") %>%
  filter(country %in% top_countries) %>%
  unnest(listed_in) %>%
  count(country, listed_in, sort = TRUE) %>%
  group_by(country) %>%
  slice_max(n, n = 5) %>%
  ungroup()
```

3) IMDb Ratings by Country
We assessed how average ratings vary across countries.
```{r}
ratings_summary <- titles_clean %>%
  unnest(production_countries) %>%
  filter(!is.na(tmdb_score)) %>%
  mutate(production_countries = str_remove_all(production_countries, "\\[|\\]|'|\"")) %>%
  group_by(production_countries) %>%
  summarise(
    avg_rating = mean(tmdb_score, na.rm = TRUE),
    n_titles = n()
  ) %>%
  filter(n_titles >= 20) %>%
  arrange(desc(avg_rating))
```

4) Star Power Impact
I tested whether movies featuring top actors received better ratings.
```{r}
netflix_data <- left_join(titles, credits, by = "id")

top_actors <- netflix_data %>%
  filter(toupper(role) == "ACTOR") %>%
  count(name, sort = TRUE) %>%
  slice_max(n, n = 50)

actor_data <- netflix_data %>%
  filter(toupper(role) == "ACTOR") %>%
  mutate(top_actor = name %in% top_actors$name)

movie_level_data <- actor_data %>%
  group_by(id, imdb_score) %>%
  summarise(any_top_actor = any(top_actor), .groups = "drop")
```

5) Text Analysis of Descriptions
I compared language used in high-rated vs. low-rated descriptions.
```{r}
desc_data <- titles %>%
  filter(!is.na(description), !is.na(imdb_score)) %>%
  mutate(
    rating_group = case_when(
      imdb_score >= 7.5 ~ "High-rated",
      imdb_score <= 5 ~ "Low-rated",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(rating_group))

word_tokens <- desc_data %>%
  unnest_tokens(word, description) %>%
  anti_join(stop_words, by = "word") %>%
  filter(str_detect(word, "^[a-z']+$"))

word_counts <- word_tokens %>%
  count(rating_group, word, sort = TRUE) %>%
  group_by(rating_group) %>%
  slice_max(n, n = 15)
```

6) Movies vs. Series: Which Rates Higher?
Finally I compared IMDb ratings between TV series and movies
```{r}
type_comparison <- titles %>%
  filter(type %in% c("MOVIE", "SHOW"), !is.na(imdb_score)) %>%
  mutate(type = factor(type, levels = c("MOVIE", "SHOW")))

type_comparison %>%
  group_by(type) %>%
  summarise(
    avg_rating = mean(imdb_score, na.rm = TRUE),
    median_rating = median(imdb_score, na.rm = TRUE),
    count = n()
  )
```

\newpage
## Question 4: Billionaires

This question explored the validity of two claims made during a Forbes panel on global billionaires:
1. The rise of self-made billionaires in the United States.
2. The shift in dominant sectors producing these billionaires.

# Load the libraries 
```{r}
library(readr)
library(readxl)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(ggplot2)
library(knitr)
library(gt)
```

# Load the data
```{r}
billionaires <- read_csv("Question 4/Data/Billions/billionaires.csv")
glimpse(billionaires)
```

# Cleaning and preparing the data
```{r}
billionaires_clean <- billionaires %>%
  filter(!is.na(year), !is.na(location.citizenship)) %>%
  mutate(
    decade = paste0(floor(year / 10) * 10, "s"),
    company.relationship = str_to_lower(company.relationship),
    company.sector = str_to_title(company.sector),
    country = str_to_upper(location.citizenship)
  )
```

# Evaluating Claim 1 :
I examined inheritence types over decades in the United states 
```{r}
us_inheritance_trends <- billionaires_clean %>%
  filter(country == "UNITED STATES") %>%
  group_by(decade, wealth.how.inherited) %>%
  summarise(n = n(), .groups = "drop") %>%
  mutate(share = round(n / sum(n), 2))
```

Plotting and saving the results 
```{r}
ggplot(us_inheritance_trends, aes(x = decade, y = share, fill = wealth.how.inherited)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    title = "US Billionaires by Inheritance Type Across Decades",
    x = "Decade",
    y = "Proportion of Billionaires",
    fill = "Inheritance Status"
  ) +
  theme_minimal()

ggsave("Question 4/Figures/us_billionaire_inheritance_by_decade.png", 
       width = 10, height = 6, dpi = 300)
```

# Claim 2 : Shift in Sectors of Self-Made Billionaires 
First identify the top sectors and group all others as "other"
```{r}
top_sectors <- billionaires_clean %>%
  filter(wealth.how.inherited == "not inherited") %>%
  count(company.sector, sort = TRUE) %>%
  slice_head(n = 8) %>%
  pull(company.sector)

billionaires_clean <- billionaires_clean %>%
  mutate(
    simplified_sector = ifelse(company.sector %in% top_sectors, company.sector, "Other")
  )
```

Then, visualize sector trends by decade and save :
```{r}
selfmade_sector_trends <- billionaires_clean %>%
  filter(wealth.how.inherited == "not inherited") %>%
  group_by(decade, simplified_sector) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(decade) %>%
  mutate(share = n / sum(n))

ggplot(selfmade_sector_trends, aes(x = decade, y = share, fill = simplified_sector)) +
  geom_col(position = "fill") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    title = "Main Sectors of Self-Made Billionaires Across Decades",
    x = "Decade",
    y = "Proportion of Self-Made Billionaires",
    fill = "Sector"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 9), legend.position = "bottom")

ggsave("Question 4/Figures/self_made_sectors_by_decade.png", 
       width = 10, height = 6, dpi = 300)
```

I also present a table summarizing the top company sectors for self-made billionaires per decade and save it : 
```{r}
top_sectors_table <- billionaires_clean %>%
  filter(
    wealth.how.inherited == "not inherited",
    !is.na(company.sector)
  ) %>%
  group_by(decade, company.sector) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(decade) %>%
  slice_max(order_by = count, n = 5, with_ties = FALSE) %>%
  ungroup() %>%
  pivot_wider(names_from = decade, values_from = count, values_fill = 0)

top_sectors_table %>%
  gt() %>%
  tab_header(
    title = "Split of Top Company Sectors for Self-Made Billionaires by Decade"
  ) %>%
  gtsave("Question 4/Figures/top_self_made_sectors_fixed.png")
```

\newpage
# Question 5 : Weight and Lifestyle Factors
In this final analysis, the goal was to derive simple, practical public health insights from a health dataset. The focus was on how sleep, physical activity, and stress levels relate to final body weight.

I explored the data visually and statistically to support a concise presentation suitable for a TV audience.

Loading required libraries 
```{r}
library(readr)
library(readxl)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(ggplot2)
```

Loading the dataset 
```{r}
health <- read_csv("Question 5/Data/Health/HealthCare.csv")
glimpse(health)
```

Sleep and Activity vs Final Weight
I used a boxplot to visualize how sleep quality and physical activity level jointly relate to final weight.
```{r}
ggplot(health, aes(x = `Sleep Quality`, y = `Final Weight (lbs)`, fill = `Physical Activity Level`)) +
  geom_boxplot() +
  labs(
    title = "Final Weight by Sleep Quality and Activity Level",
    x = "Sleep Quality", y = "Final Weight (lbs)", fill = "Activity Level"
  ) +
  theme_minimal()
ggsave("Question 5/Figures/final_weight_by_sleep_and_activity.png",
       width = 10, height = 6, dpi = 300)
```

\newpage
Stress and Weight Across Activity Levels
I tested whether stress levels impact final weight beyond activity and sleep, To show this I created a jitter plot with a regression line.
Loading and exploring the data 
```{r}
ggplot(health, aes(x = `Stress Level`, y = `Final Weight (lbs)`)) +
  geom_jitter(aes(color = `Physical Activity Level`), width = 0.3, alpha = 0.7, size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linetype = "dashed") +
  labs(
    title = "Impact of Stress and Activity on Final Weight",
    subtitle = "Stress level vs final weight across different activity levels", 
    x = "Stress Level (1 = Low, 10 = High",
    y = "Final Weight (lbs)",
    color = "Activity Level"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(margin = margin(b = 10))
  )

ggsave("Question 5/Figures/Impact of Stress and Activity on Final Weight.png",
       width = 10, height = 6, dpi = 300)
```

Linear Regression Model
I modeled Final Weight as a function of:

- Sleep Quality

- Physical Activity Level

- Stress Level

- Duration (weeks)
```{r}
health_clean <- health %>%
  mutate(
    `Sleep Quality` = as.factor(`Sleep Quality`),
    `Physical Activity Level` = as.factor(`Physical Activity Level`)
  )

# Run the linear model
model <- lm(
  `Final Weight (lbs)` ~ `Sleep Quality` + `Physical Activity Level` + `Stress Level` + `Duration (weeks)`,
  data = health_clean
)

# View summary
summary(model)
```


